Paper Analysis

### 2025-05-29 Paper_WriteUp/Reviewer_Response.qmd

## to load some plot defaults
source(here("utils", "helper.R"))
source(here("utils", "plot_templates.R"))

all_data_path <- rep(NA, 4)
all_data_path[1] <- here("box_data/lichess1700-1900/")
all_data_path[2] <- here("box_data/lichess2000-2200/")
all_data_path[3] <- here("box_data/lichess2300-2500/")
all_data_path[4] <- here("box_data/lichessGrandmasters/")
res_data_path <- rep(NA, 4)
res_data_path[1] <- here("results_2025/lichess1700-1900/")
res_data_path[2] <- here("results_2025/lichess2000-2200/")
res_data_path[3] <- here("results_2025/lichess2300-2500/")
res_data_path[4] <- here("results_2025/lichessGrandmasters/")

```

#Associate Editor, Comment 5 - plotting RDs and volatilities
```{r}
#import data
data_path = paste0(all_data_path[4])

@@

#save
ggsave(plot = RD_plot,
       filename = here("Paper_WriteUp", "paper_figures", "response to comments", "RDs.png"), dpi = 1000,
       height = 6, width = 8)

#volatilities
vol_plot = ggplot(data = init_RDs %>% group_by(focal_user) %>% mutate(index = row_number()), mapping = aes(x = index, y = volatility)) +
  geom_line() +
  scale_x_continuous(n.breaks = 3, limits = c(0, 5000)) +
  #scale_y_continuous(limits = c(0.04, 0.06)) +
  labs(x = "Game Number", y = "Rating Deviation") +
  facet_wrap(~focal_user)

#save
ggsave(plot = vol_plot,
       filename = here("Paper_WriteUp", "paper_figures", "response to comments", "volatilities.png"), dpi = 1000,
       height = 6, width = 8)
```

#Reviewer 2, Comment 6 - distribution of x_{ij}
```{r}
#import data
data_path = paste0(all_data_path[1], "/")
